---
title: "00_simple rf"
format: html
editor: visual
---

## Building intuition with complexity

Steps in this document:

-   Build a **simple RF** containing exposures (PM2.5, O3, NO2, heat) during the first 20 weeks of pregnancy. Use spatial cross-validation. The outcome is placental insufficiency (note: sensitivity to the defining criteria will be assessed separately).

    -   [Side note:]{.underline} maybe ensure that each exposure actually improves the model fit?

-   **Extend** the simple RF to include confounders (not proper adjustment). Interpret variable importance, etc., and **compare model fit** against the first RF model.

-   **Extend** the simple random forest to include spatial and temporal basis functions. Interpret variable importance, etc., and **compare model fit** against the previous two models.

Next steps will be to run the RF with a long structure, i.e., person-time, to analyze all weeks of exposure. This will allow for time-to-event analysis. Then we'll go causal. (And separately, we'll use Cox proportional hazard.)

## Step 1. Prepare data for exposure model

...

```{r}

```

...

## Step 2. Exposure-only RF

```{r}

```






